A family of accessibility measures derived from spatial interaction principles

### 2025-10-22 paper_plos/summary-family-access-measures-table.tex
V3 AS revision; small gramar changes here and there.

{\tiny
\begin{longtable}{|p{2.5cm}|p{2.5cm}|p{2.5cm}|p{3cm}|p{3cm}|}
\hline
\textbf{Name of Member and Variant} & \textbf{Constraint Explanation and Balancing Factor} & \textbf{Proportional Allocation Factor} & \textbf{Measure Equation} & \textbf{Interpretation} \\
\hline
\endfirsthead

\hline
\textbf{Name of member and Variant} & \textbf{Constraint Explanation and Balancing Factor} & \textbf{Proportional Allocation Factor} & \textbf{Measure Equation} & \textbf{Interpretation} \\
\hline
\endhead

@@

& Values in various units depending on the impedance and destination-mass (e.g., "opportunities x decay") for $V_i^0$ andimpedance and origin-mass (e.g., "population x decay"); no total or marginal constraint \\
\hline

@@

& Values reflect a share of total regional opportunities ($V^T_i$) or population ($M^T_j$). \\
\hline

@@

& $V^S_i$ values reflect a share of the opportunities at each destination based on origin population 'demand' and impedance; $M^S_j$ values reflect a share of the population at each origin based on destination opportunities 'supply' and impedance.\\
\hline

>>>>

{\tiny
\begin{longtable}{|p{2.5cm}|p{2.5cm}|p{2.5cm}|p{3cm}|p{3cm}|}
\hline
\textbf{Name of Member and Variant} & \textbf{Constraint Explanation and Balancing Factor} & \textbf{Proportional Allocation Factor} & \textbf{Accessibility Measure Equation} & \textbf{Interpretation} \\
\hline
\endfirsthead

\hline
\textbf{Name of member and Variant} & \textbf{Constraint Explanation and Balancing Factor} & \textbf{Proportional Allocation Factor} & \textbf{Accessibility Measure Equation} & \textbf{Interpretation} \\
\hline
\endhead

@@

& Values in various units depending on the impedance and destination-mass (e.g., "opportunities x decay") for $V_i^0$ and impedance and origin-mass (e.g., "population x decay") for $M_j^0$; no total or marginal constraint \\
\hline

@@

& Values reflect a share of the total opportunities in the region $D$ for $V^T_i$ or total population in the region $O$ for $M^T_j$. \\
\hline

@@

& $V^S_i$ values reflect a share of the opportunities at each destination $D_j$ based on origin population 'demand' and impedance; $M^S_j$ values reflect a share of the population at each origin $O_i$ based on destination opportunities 'supply' and impedance.\\
\hline
